# (PART) Cross Tabulation Graphs {-}
# Single Country Overall Graphs {#chapter-1}

This chapter will cover how to make an overall frequency graph for a single country.

## Create a Single Graph

This section will go over how to make a one-off frequency graph for a single country.

At the end, your code will look like the following:

```{r 01.1-Complete-Code-Example, eval=FALSE}

survey1 %>%
  calculate_smry_individual("Q1COVID19",
                            "Algeria") %>%
  plot_smry_individual(.caption = "Arab Barometer Wave VI, Survey I, Algeria")


```

That code will produce the following graph:


```{r 01.2-Complete-Graph-Example, echo=FALSE, fig.dim=c(13,12),cache=TRUE}

survey1 %>%
  calculate_smry_individual("Q1COVID19",
                            "Algeria") %>%
  plot_smry_individual(.country = "Algeria",
                       .caption = "Arab Barometer Wave VI, Survey I")


```

Let's go!

### Create a Summary

The first step in creating a plot is to gather the data you want to display and organize it. You do this with the **create_smry_individual()** function.

The three main parameters you need to provide to this function are (1) the data you are using, (2) the variable you want to plot, and (3) the country you want to plot it for. To see all the input parameters for the function, type the code `?calculate_smry_individual` in your R console.

In this example, the variable we want to plot is **Q1COVID19** and the country we want to plot it for is **Algeria**.

```{r 01.3-summary, eval=FALSE}

calculate_smry_individual(
  .ab = survey1,            # The data you are using
  .var = "Q1COVID19",       # The variable you want to plot
  .country = "Algeria"      # The country you want to plot it for
)

```

The above is the same as:

```{r 01.4-summary, eval=FALSE}

calculate_smry_individual(survey1,"Q1COVID19","Algeria")

```

Which is the same as:


```{r 01.5-summary, eval=FALSE}


survey1 %>%
  calculate_smry_individual("Q1COVID19",
                            "Algeria")

```

The last example uses a pipe, `%>%`, which comes from the package **dplyr**, which is automatically loaded by `ArabBarometR`. To learn more about piping and using `%>%` in programming, see [A Note on Piping](https://arab-barometer.github.io/ArabBarometR-Guide/using-the-package.html#a-note-on-piping) in the larger `ArabBarometR` guide.

The output of any of the above expressions is the same:

```{r 01.6-summary, echo=FALSE}


survey1 %>%
  calculate_smry_individual("Q1COVID19",
                            "Algeria")

```

This data frame is what we are ultimately graphing.

There are few things to note about the summary data frame we just created.

First, there are two columns. The first column is named for the question we are graphing. The second column is named **Percent**. If you want to use the plotting functions in `ArabBarometR` to graph a summary data frame that is not created by a calculate function (see [complete list of calculate functions](https://arab-barometer.github.io/ArabBarometR-Guide/calculating-summaries.html) in the `ArabBarometR` Guide), the data frame must be structured as two columns with the second column named **Percent**.

Second, you can see that the first column is labeled. The labels come from the responses in the data. If the responses in the data are not labeled, this column will not be labeled. In the next step, plotting, the y-axis labels are taken from these labels. So, if the column is not labeled, the y-axis will just be the values of the column.

Let's store the summary as an object and move on.

```{r 01.7-summary, eval=FALSE}


Q1COVID19_summary <- survey1 %>%
  calculate_smry_individual("Q1COVID19",
                            "Algeria")

```

### Plot the Summary

The next step is plot the summary we just created. To do this, we use the function **plot_smry_individual()**.

There is only *one* necessary parameter to use **plot_smry_individual()**: the summary data frame. For a complete list of acceptable parameters and documentation, you can run `?plot_smry_individual` in your R console.

Now, we can plug our summary into the plot function:

```{r 01.8-plot, eval=FALSE}

plot_smry_individual(
  .df = Q1COVID19_summary  # The summary data frame
)

```

The above code is the same as:

```{r 01.9-plot, eval=FALSE}

Q1COVID19_summary %>%
  plot_smry_individual()

```

Which is the SAME as:

```{r 01.10-plot, eval=FALSE}

survey1 %>%
  calculate_smry_individual("Q1COVID19",
                            "Algeria") %>%
  plot_smry_individual()


```

We can do this because `Q1COVID19_summary` is equal to `survey1 %>% calculate_smry_individual("Q1COVID19", "Algeria")`.


Any of the above code gives the following graph:


```{r 01.11-plot, echo=FALSE, fig.dim=c(13,12),cache=TRUE}

survey1 %>%
  calculate_smry_individual("Q1COVID19",
                            "Algeria") %>%
  plot_smry_individual()


```


Almost done! Notice how the caption says **Arab Barometer Wave N (DATE)**? Let's change that.


```{r 01.12-plot, eval=FALSE}

survey1 %>%
  calculate_smry_individual("Q1COVID19",
                            "Algeria") %>%
  plot_smry_individual(
    .caption = "Arab Barometer Wave VI, Survey I, Algeria"  # NEW caption
  )


```

Now we have the plot we started with! We're done!


```{r 01.13-plot, echo=FALSE, fig.dim=c(13,12),cache=TRUE}

survey1 %>%
  calculate_smry_individual("Q1COVID19",
                            "Algeria") %>%
  plot_smry_individual(
    .caption = "Arab Barometer Wave VI, Survey I, Algeria"  # NEW caption
  )


```



## Create Many Graphs

As a rule of thumb in programming, if you can create something one time, you can create it a bajillion times. This is good because for each wave, Arab Barometer needs approximately a bajillion graphs.

To create many graphs at once, there are three steps to follow.

1. First, identify the variables to plot.
2. Second, create summaries of those variables.
3. Third, plot those summaries.

At the end of this section, your code will look like the following:


```{r 01.14-Complete-Code-Example, eval=FALSE}

     #.....................Identify the variables.....................
variables_2_plot <- list("Q1COVID19",
                         "Q2061A",
                         "Q609")

names(variables_2_plot) <- c("Q1COVID19",
                             "Q2061A",
                             "Q609")

     #......................Create the summaries......................
summaries <- survey1 %>%
  calculate_smry_individual(variables_2_plot,
                            "Algeria") 

     #.......................Plot the summaries.......................
plots <- map(summaries,
             plot_smry_individual,
             .caption = "Arab Barometer Wave VI, Survey I")

```

The result is a named list of plots. Each element in the list is a plot. The element is named for the variable it is a plot of.

For example, to see the plot for variable `Q1COVID19`, run the following code:


```{r 01.14.5-Complete-Code-Example, echo=FALSE,cache=TRUE}

     #.....................Identify the variables.....................
variables_2_plot <- list("Q1COVID19",
                         "Q2061A",
                         "Q609")

names(variables_2_plot) <- c("Q1COVID19",
                             "Q2061A",
                             "Q609")

     #......................Create the summaries......................
summaries <- survey1 %>%
  calculate_smry_individual(variables_2_plot,
                            "Algeria") 

     #.......................Plot the summaries.......................
plots <- map(summaries,
             plot_smry_individual,
             .caption = "Arab Barometer Wave VI, Survey I")

```


```{r 01.15-Complete-Code-Example-Results1, fig.dim=c(13,12),cache=TRUE}

plots$Q1COVID19

```

To see the plot for variable `Q2061A`, run the following code:

```{r 01.16-Complete-Code-Example-Results2, fig.dim=c(13,12),cache=TRUE}

plots$Q2061A

```

Finally, to see the plot for variable `Q609`, run the following code:

```{r 01.17-Complete-Code-Example-Results3, fig.dim=c(13,12),cache=TRUE}

plots$Q609

```

That's it! The only limit on the number of graphs you can create at once is the time it will take R to make them. The more graphs you try to create at once, the longer it will take.

Let's begin.

### Identify the Variables

When creating many graphs, you need to tell R which variables you want to make plots of. This is true for when you want to create a single graph as well, but it is much more strongly implied. Plus, the variables must be identified in a specific way.

To create many summaries at once, you need to provide your variables in a named list. To create a named list, first make a list of the variables you want to plot.

```{r 01.18-list, eval=FALSE}

variables_2_plot <- list("Q1COVID19",
                         "Q2061A",
                         "Q609")

```

The next step is to name your list.

```{r 01.19-named-list, eval=FALSE}

names(variables_2_plot) <- c("Q1COVID19",
                             "Q2061A",
                             "Q609")

```

Now, you have a named list of variables. Time to summarize them.

### Create Summaries

The same function used to create a single summary is used to create many summaries: **calculate_smry_individual()**. Recall it takes three parameters: (1) the data you are using, (2) the variable(s) you want to plot, and (3) the country you are creating the plot for. Now, instead of one variable, you supply the list of variables.

```{r 01.20-summaries, eval=FALSE}

calculate_smry_individual(
  .ab = survey1,               # The data you are using
  .var = variables_2_plot,       # The variables you want to plot
  .country = "Algeria"           # The country you want to plot it for
)

```

The above is the same as:

```{r 01.21-summaries, eval=FALSE}

calculate_smry_individual(survey1,variables_2_plot,"Algeria")

```

Which is the same as:


```{r 01.22-summaries, eval=FALSE}


survey1 %>%
  calculate_smry_individual(variables_2_plot,
                            "Algeria")

```


All of the above code in this section produces the same result: a named list. Each element in the list is a summary of a variable. The variable is the name of the list. In long form, it looks like the following:

```{r 01.23-summaries, echo=FALSE,cache=TRUE}


survey1 %>%
  calculate_smry_individual(variables_2_plot,
                            "Algeria")

```

Let's save this outcome as an object and move on to plotting.


```{r 01.24-summaries, eval=FALSE}


summaries <- survey1 %>%
  calculate_smry_individual(variables_2_plot,
                            "Algeria")

```


### Plot the Summaries

Again, the same function to create one plot is used to create many plots: **plot_smry_individual()**. Unlike last time, a helper function is needed to create multiple plots. 

The helper function is called **map**. The map function takes two inputs: (1) a list of things to pass to a function, and (2) a function. Essentially, **map** takes each item in the list, and passes it to the function very efficiently. 

In this case, you supply the list of summaries you just created, and the **plot_sumry_individual()** function. The code follows:

```{r 01.25-plots, eval=FALSE}

map(
  summaries,            # List of summaries
  plot_smry_individual  # Plotting function
)

```
The code produces the following output:

```{r 01.26-plots, figures-side, fig.show="hold", out.width="50%",cache=TRUE}
map(
  summaries,            # List of summaries
  plot_smry_individual  # Plotting function
)

```


Notice, yet again, the caption needs to be changed. To change the caption for all the graphs, just add one line to the map function.


```{r 01.27-plots, figures-side, fig.show="hold", out.width="50%",cache=TRUE}
map(
  summaries,                                     # List of summaries
  plot_smry_individual,                          # Plotting function
  .caption = "Arab Barometer Wave VI, Survey I"  # Caption
)

```


Congratulations! You have created three plots at once. You can store them in as a single list and call them one at a time.

```{r 01.28-plots, eval=FALSE}
plots <- map(
  summaries,                                     # List of summaries
  plot_smry_individual,                          # Plotting function
  .caption = "Arab Barometer Wave VI, Survey I"  # Caption
)

```


```{r 01.28.5-plots, echo=FALSE,cache=TRUE}
plots <- map(
  summaries,                                     # List of summaries
  plot_smry_individual,                          # Plotting function
  .caption = "Arab Barometer Wave VI, Survey I"  # Caption
)

```

Now, all three plots have been stored in a named list named `plots`. To look at the first plot:

```{r 01.29-Complete-Code-Example-Results1, fig.dim=c(13,12),cache=TRUE}

plots$Q1COVID19

```

To see the plot for variable `Q2061A`, run the following code:

```{r 01.30-Complete-Code-Example-Results2, fig.dim=c(13,12),cache=TRUE}

plots$Q2061A

```

Finally, to see the plot for variable `Q609`, run the following code:

```{r 01.31-Complete-Code-Example-Results3, fig.dim=c(13,12),cache=TRUE}

plots$Q609

```


You have now completed all steps in the example code. Congrats!

