# Single Country Demographic Plots

This chapter will cover how to make a frequency graph by a demographic for a single country.

**This code assumes you have already added the demographic variables to your code.** See the section [Header Code](#headercode) in the introduction.

## Create a Single Graph

This section will go over how to make a one-off frequency graph by a demographic for a single country.

At the end, your code will look like the following:

```{r 02.1-Complete-Code-Example, eval=FALSE}

survey1 %>%
  calculate_demographic_smry_individual("Q1COVID19",
                                        "gender",
                                        "Algeria") %>%
  plot_demographic_smry_individual(.caption = "Arab Barometer Wave VI, Survey I, Algeria")


```

That code will produce the following graph:


```{r 02.2-Complete-Graph-Example, echo=FALSE, fig.dim=c(13,12)}

survey1 %>%
  calculate_demographic_smry_individual("Q1COVID19",
                                        .dem = "gender",
                                        .country = "Algeria") %>%
  plot_demographic_smry_individual(.caption = "Arab Barometer Wave VI, Survey I, Algeria")

```

Notice these messages and warnings? That's ok! You can ignore them. In the rest of this chapter, the messages and warning will be silenced. They are shown here to make sure the reader knows nothing is wrong if you see them.

### Creating a Summary

The first step in creating a plot is to gather the data you want to display and organize it. You do this with the `calculate_demographic_smry_individual()` function.

Just like `calculate_smry_individual()`, the four main parameters you need to provide to this function are (1) the data you are using, (2) the variable you want to plot, (3) the demographic you want to divide the variable by, and (4) the country you want to plot it for. To see all the input parameters for the function, type the code `?calculate_demographic_smry_individual` in your R console.

In this example, the variable we want to plot is `Q1COVID19`, the demographic we want to compare is `gender`, and the country we want to plot it for is **Algeria**^[If the style of this code is confusing, see [Create a Summary in Chapter 1][Single Country Overall Graphs]].

```{r 02.3-summary, eval=FALSE}

survey1 %>%                                                    # Data
  calculate_demographic_smry_individual("Q1COVID19",           # Variable to summarize  
                                        .dem = "gender",       # Demographic
                                        .country = "Algeria")  # Country

```

The above code will produce the following output:


```{r 02.4-summary, echo=FALSE,warning=FALSE,message=FALSE}

survey1 %>%                                                    # Data
  calculate_demographic_smry_individual("Q1COVID19",           # Variable to summarize  
                                        .dem = "gender",       # Demographic
                                        .country = "Algeria")  # Country

```

The function `calcuate_demographic_smry()` creates a named list. In this list, each item is a summary broken down by a demographic and the name of each item is that demographic.

Let's save our gender demographic summary and move on to plotting it.

```{r 02.7-summary, eval=FALSE}

Q1COVID19_gender <- survey1 %>%
  calculate_demographic_smry_individual("Q1COVID19",
                                        .dem = "gender",
                                        .country = "Algeria")

```


```{r 02.8-summary, echo=FALSE,warning=FALSE,message=FALSE}

Q1COVID19_gender <- survey1 %>%
  calculate_demographic_smry_individual("Q1COVID19",
                                        .country = "Algeria",
                                        .dem = "gender")

```


### Plotting the Summary


The next step is plot the summary we just created. To do this, we use the function `plot_demographic_smry_individual()`.

There is only *one* necessary parameter to use `plot_smry_individual()`: the summary data frame. For a complete list of acceptable parameters and documentation, you can run `?plot_demographic_smry_individual` in your R console.

Now, we can plug our summary into the plot function:

```{r 02.9-plot, eval=FALSE}

plot_demographic_smry_individual(Q1COVID19_gender)

```

The above code is the same as:

```{r 02.10-plot, eval=FALSE}

Q1COVID19_gender %>%
  plot_demographic_smry_individual()

```

Both stylings of code produce the following graph:

```{r 02.11-plot, echo=FALSE, fig.dim=c(13,12),warning=FALSE,message=FALSE}

plot_demographic_smry_individual(Q1COVID19_gender)

```

Yet again, we see the caption needs to be changed. We can change it the same way we did in Chapter 1.

```{r 02.12-plot, eval=FALSE}

Q1COVID19_gender %>%
  plot_demographic_smry_individual(
    .caption = "Arab Barometer Wave VI, Survey I, Algeria"
  )

```

Now we have the graph:

```{r 02.13-plot, echo=FALSE, fig.dim=c(13,12),warning=FALSE,message=FALSE}

Q1COVID19_gender %>%
  plot_demographic_smry_individual(
    .caption = "Arab Barometer Wave VI, Survey I, Algeria"
  )


```


Since `Q1COVID19_gender` is the same as `survey1 %>% calculate_demographic_smry_individual("Q1COVID19","gender","Algeria")`, we can substitute the former with the latter to get the original code in our example. This will give us the same plot that we just created.

```{r 02.14-plot, eval=FALSE}

survey1 %>%
  calculate_demographic_smry_individual("Q1COVID19",
                                        "gender",
                                        "Algeria") %>%
  plot_demographic_smry_individual(.caption = "Arab Barometer Wave VI, Survey I, Algeria")



```


## Create Many Graphs

We will follow the same steps from Chapter one to create many graphs at once.

1. First, identify the variables to plot.
2. Second, create summaries of those variables.
3. Third, plot those summaries.

At the end of this section, your code will look like the following:


```{r 02.15-Complete-Code-Example, eval=FALSE}

     #.....................Identify the variables.....................
variables_2_plot <- list("Q1COVID19",
                         "Q2061A",
                         "Q609")

names(variables_2_plot) <- c("Q1COVID19",
                             "Q2061A",
                             "Q609")

     #......................Create the summaries......................
gender_summaries <- survey1

gender_summaries <- survey1 %>%
  calculate_demographic_smry_individual(variables_2_plot,
                                        "gender",
                                        "Algeria") 

     #.......................Plot the summaries.......................
gender_plots <- map(gender_summaries,
                    plot_demographic_smry_individual,
                    .caption = "Arab Barometer Wave VI, Survey I")

```

The result is a named list of plots. Each element in the list is a plot. The element is named for the variable it is a plot of.

For example, to see the plot for variable `Q1COVID19`, run the following code:


```{r 02.16-Complete-Code-Example, echo=FALSE,warning=FALSE,message=FALSE}

     #.....................Identify the variables.....................
variables_2_plot <- list("Q1COVID19",
                         "Q2061A",
                         "Q609")

names(variables_2_plot) <- c("Q1COVID19",
                             "Q2061A",
                             "Q609")

     #......................Create the summaries......................
gender_summaries <- survey1 %>%
  calculate_demographic_smry_individual(variables_2_plot,
                                        "gender",
                                        "Algeria") 

     #.......................Plot the summaries.......................
gender_plots <- map(gender_summaries,
                    plot_demographic_smry_individual,
                    .caption = "Arab Barometer Wave VI, Survey I")

```


```{r 02.17-Complete-Code-Example-Results1, fig.dim=c(13,12),warning=FALSE,message=FALSE}

gender_plots$Q1COVID19

```

To see the plot for variable `Q2061A`, run the following code:

```{r 02.18-Complete-Code-Example-Results2, fig.dim=c(13,12),warning=FALSE,message=FALSE}

gender_plots$Q2061A

```

Finally, to see the plot for variable `Q609`, run the following code:

```{r 02.19-Complete-Code-Example-Results3, fig.dim=c(13,12),warning=FALSE,message=FALSE}

gender_plots$Q609

```

That's it! The only limit on the number of graphs you can create at once is the time it will take R to make them. The more graphs you try to create at once, the longer it will take.

The steps to creating a named variable list are exactly the same as the ones we reviewed in Chapter 1; therefore, we will begin by creating summaries. For a refresher on creating named lists, [click here][Identify the Variables]. We will use the same variables as in Chapter 1: `Q1COVID19`, `Q2061A`, and `Q609`.

Let's begin.

### Create Summaries

The same function used to create a single summary is used to create many summaries: `calculate_demographic_smry_individual()`. Recall it takes four parameters: (1) the data you are using, (2) the variable(s) you want to plot, (3) the demographic you want the data summarized by and (4) the country you are creating the plot for. Now, instead of one variable, you supply the list of variables.

```{r 02.20-summaries, eval=FALSE}

survey1 %>%                                               # Data
  calculate_demographic_smry_individual(variables_2_plot, # Variables to summarize
                                        "gender",         # Demographic
                                        "Algeria")        # Country

```

The above code produces a nested named list. Each element in the list is another named list. Each element in the outer list is named for a variable you want to create summaries for. The inner list of each element is a summary with the data grouped by `age`, `gender`, `income`, and `education`. You can think of it like the following bullet point list:

* `calculate_demographic_smry_individual` output
  * `Q1COVID19`
    * `gender` Q1COVID19 summary grouped by gender
  * `Q2061A`
    * `gender` Q2061A summary grouped by gender
  * `Q609`
    * `gender` Q609 summary grouped by gender

Let's save this outcome as an object and move on to plotting.


```{r 02.22-summaries, eval=FALSE, message=FALSE}

gender_summaries <- survey1 %>%                                               
  calculate_demographic_smry_individual(variables_2_plot, 
                                        "gender",
                                        "Algeria")  

```



```{r 02.23-summaries, echo=FALSE}

gender_summaries <- survey1 %>%                                               
  calculate_demographic_smry_individual(variables_2_plot, 
                                        "gender",
                                        "Algeria")  

```


### Plot the Summaries {#plot-many-graphs-single-country-demographic}

Again, the same function to create one plot is used to create many plots: `plot_demographic_smry_individual()`. Just like in Chapter 1, we need to use the `map` function.

In this case, you supply the list of summaries you just created, and the `plot_demographic_sumry_individual()` function. The code follows:

```{r 02.24-plots, eval=FALSE}

map(
  gender_summaries,                        # List of summaries
  plot_demographic_smry_individual         # Plotting function
)

```

The code produces the following output:

```{r 02.25-plots, figures-side, fig.show="hold", out.width="50%",warning=FALSE,message=FALSE}

map(
  gender_summaries,                       # List of summaries
  plot_demographic_smry_individual         # Plotting function
)

```


Notice, yet again, the caption needs to be changed. To change the caption for all the graphs, just add one line to the map function.


```{r 02.26-plots, figures-side, fig.show="hold", out.width="50%",warning=FALSE,message=FALSE}
map(
  gender_summaries,                              # List of summaries
  plot_demographic_smry_individual,              # Plotting function
  .caption = "Arab Barometer Wave VI, Survey I"  # Caption
)

```


Congratulations! You have created three plots at once. You can store them in as a single list and call them one at a time.

```{r 02.27-plots, eval=FALSE}

gender_plots <- map(
  gender_summaries,                              # List of summaries
  plot_demographic_smry_individual,              # Plotting function
  .caption = "Arab Barometer Wave VI, Survey I"  # Caption
)

```


```{r 02.28-plots, echo=FALSE}

gender_plots <- map(
  gender_summaries,                              # List of summaries
  plot_demographic_smry_individual,              # Plotting function
  .caption = "Arab Barometer Wave VI, Survey I"  # Caption
)

```

Now, all three plots have been stored in a named list named `gender_plots`. To look at the first plot:

```{r 02.29-Complete-Code-Example-Results1, fig.dim=c(13,12),warning=FALSE,message=FALSE}

gender_plots$Q1COVID19

```

To see the plot for variable `Q2061A`, run the following code:

```{r 02.30-Complete-Code-Example-Results2, fig.dim=c(13,12),warning=FALSE,message=FALSE}

gender_plots$Q2061A

```

Finally, to see the plot for variable `Q609`, run the following code:

```{r 02.31-Complete-Code-Example-Results3, fig.dim=c(13,12),warning=FALSE,message=FALSE}

gender_plots$Q609

```


You have now completed all steps in the example code. Congrats!