# Single Country Trend Graphs {#chapter-5}

This chapter will cover how to create trend graphs for one country. Prior to this, we have only used a single data set, `survey1`. We will now also use the data sets `survey2` and `survey3`. Refer to the assumed [header code](#headercode) to see where `survey1`, `survey2`, and `survey3` came from.

## TL;DR {-}

At the end, your code will look like the following:

```{r 05.1-Complete-Code-Example, eval=FALSE}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

calculate_ind_trend("Q1COVID19",
                    df_list,
                    survey_dates,
                    "Algeria") |> 
  plot_ind_trend(.caption = "Arab Barometer Wave VI, Algeria")


```

The code produces this graph:

```{r 05.2-Complete-Graph-Example, echo=FALSE, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

calculate_ind_trend("Q1COVID19",
                    df_list,
                    survey_dates,
                    "Algeria") |> 
  plot_ind_trend(.caption = "Arab Barometer Wave VI, Algeria")



```

Let's go!

## Prep Work {#chapter-5-1-1}

It is useful to do some prep work to keep everything clear. Just as we did some prep work for multi-question graphs in Chapters \@ref(new-chapter-9-1) and \@ref(chapter-10-1), we will take some pre-graph-creation steps to make our lives easier down the road.

### Create a Data Frame List {- #chp5-trend-df-list}

The first step is to create a list of data frames. 

There should be one data frame for each period you wish to graph. That is, each data frame should be from a different survey you want to include in your graph. In the example for the chapter, we're using the three surveys from Wave VI, which we call `survey1`, `survey2`, and `survey3`. Each survey is its own data frame.

```{r 05.3-Single-Trend,echo=T,eval=FALSE}

df_list <- list(
  survey1,
  survey2,
  survey3
)

```


The list of data frames should be in the order you want them to appear (ideally, chronologically). The data on the graph will show up in the order of the list. So if you create a list in the order `list(survey2, survey1, survey3)`, the data from `survey2` will show up before the data from `survey1`. 

**Please note: This is ambivalent to language!** The `plot_ind_trend()` function will assume the order of the list is the correct order, and treat it accordingly. When you enter a list as `list(survey1, survey2, surveye3)`, the English graph will show the data right to left (survey 1 -> survey 2 -> survey 3), while the Arabic graph will show the data left to right (survey 3 <- survey 2 <- survey 1). You do **not** need to alter your input.

> The data frame lists in the `Wave8TrendData` package do this step for you.

### Create a Date Vector {- #chp5-trend-date-vector}

The next step is to create a vector of the dates you want to show on the x-axis of your graph. Branding guidelines call for the years in which the survey took place. For simplicity in the example, let's just say `"Survey X Year"`. 

You need a date for each data frame in your data frame list. Otherwise, the function won't know how to label the x-axis.


```{r 05.4-Single-Trend,echo=T,eval=FALSE}

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

```

The dates should also be in the order you want them to appear. The dates should line up with the data frames. In the chapter example, the order of the data frames is survey 1, survey 2, survey 3. Therefore, the survey dates need to have the order survey 1 year, survey 2 year, survey 3 year.

**Please note: This is ambivalent to language!** Just as with the data frame list, the `plot_ind_trend()` function will put the data in the correct order according to the language of the graph.

Now that we have defined our data frame list and survey dates, we can create our trend plot.

> The date vectors in the `Wave8TrendData` package do this step for you.

## Create a Summary  {#chapter-5-1-2}

Like always, the first step in creating a graph is creating a summary. To do this for an individual trend graph, we use the function `calculate_ind_trend()`.

The function `calculate_ind_trend()` requires **four** parameters: `.var`, `data_frames`, `survey_dates`, and `select_country`. To see a complete list of parameters, including optional ones, use `?plot_trend_individual()` in your `R` console.

The parameter `.var` is the variable you want to plot. **It must have the same name in every data frame in the data frame list.** If the variable you want to plot is named `"Q101"` in one sure, but `"Q102"` in another, the function will not include `"Q102"` in the plot. Computers can do a lot but as of yet they cannot think critically, so the onus is on you.

> The trend data lists from the `Wave8TrendData` package ensure this is true for Wave VIII variables.

The parameter `data_frames` is a list of data frames. This is what we created [here](chp5-trend-df-list). 

The parameter `survey_dates` is a character vector of dates that will show up on the x-axis of the graph. This is what we created [here](chp5-trend-date-vector).

The parameter `select_country` is the name of the country you want to create the graph for.

Now let's fill it in.

```{r 05.5-1-2-1, collapse=TRUE, eval=FALSE}

calculate_ind_trend(
  .var           = "Q1COVID19",    # Variable to graph
  data_frames    = df_list,        # List of data frames
  survey_dates   = survey_dates,   # Vector of survey dates
  select_country = "Algeria"       # Country to graph
  )



```
The output should look like the following, with the `Survey` column labeled.

```{r 05.5-1-2-1-output, collapse=TRUE, echo=FALSE}
individual_trend_summary <- calculate_ind_trend(
  "Q1COVID19",    
  df_list,        
  survey_dates,   
  "Algeria"       
  )


knitr::kable(
  individual_trend_summary,
  booktabs = TRUE,
  label = NA
)


```
We can see the resulting data frame has three rows; one for each survey we are plotting. Let's save the output as an object so we can plot that object in the next section.

```{r 05.5-1-2-2, collapse=TRUE}

individual_trend_summary <- calculate_ind_trend(
  "Q1COVID19",    
  df_list,        
  survey_dates,   
  "Algeria"       
  )

```


## Plot the Summary {#chapter-5-1-3}

The next step is to plot the summary we just created. To do that, we use the function `plot_ind_trend()`.

This function only *requires* one argument: `ab_summary`. Like many other graphs, we'll want to add a bit later on. To see a complete list of parameters, including optional ones, use `?plot_ind_trend()` in your `R` console. For now, let's see what happens when we just supply our summary we saved as `individual_trend_summary`.


```{r 05.5-1-3-1,collapse=TRUE,fig.dim=c(13,12)}

plot_ind_trend(
  ab_summary = individual_trend_summary
)

```

Nearly there! What still needs to be changed?

The caption, of course! Just as in all the other `plot_` functions in the `ArabBarometR` package, you can change the caption using the `.caption` parameter.

```{r 05.5-1-3-2,collapse=TRUE,fig.dim=c(13,12)}

plot_ind_trend(
  ab_summary = individual_trend_summary,
  .caption = "Arab Barometer Wave VI, Algeria"
)

```

Putting all the steps together, we have the code and graph we originally started with.


```{r 05.9-Complete-Code-Example, echo=FALSE, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

calculate_ind_trend("Q1COVID19",
                    df_list,
                    survey_dates,
                    "Algeria") |> 
  plot_ind_trend(.caption = "Arab Barometer Wave VI, Algeria")



```

```{r 05.9.5-Complete-Code-Example, eval=FALSE}


df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

calculate_ind_trend("Q1COVID19",
                    df_list,
                    survey_dates,
                    "Algeria") |> 
  plot_ind_trend(.caption = "Arab Barometer Wave VI, Algeria")



```

## Extras 

### Font Size

The font size default brand size is used for the graph text. You can learn how to change that in [the chapter on changing the font size](#change-font-size).

### Colors

You can learn how to change the colors for the single country trend graph in [the chapter on changing graph colors](#change-colors-trend-comparative).

