# (PART) Trend Graphs {-}
# BARE BONES: Single Country Trend Graphs

This chapter will cover how to create trend graphs for one country. Prior to his, we have only used a single data set, `survey1`. We will now also use the data sets `survey2` and `survey3`. Refer to the assumed [header code](#headercode) to see where `survey1`, `survey2`, and `survey3` came from.

## Create Single Trend Graph

At the end, your code will look like the following:

```{r 05.1-Complete-Code-Example, eval=FALSE}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1",
                  "Suvey 2",
                  "Survey 3")

plot_trend_individual("Q1COVID19",
                      df_list,
                      survey_dates,
                      "Algeria")


```

The code produces this graph:

```{r 05.2-Complete-Graph-Example, echo=FALSE, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1",
                  "Suvey 2",
                  "Survey 3")

plot_trend_individual("Q1COVID19",
                      df_list,
                      survey_dates,
                      "Algeria")


```
