# Single Country Demographic Trend Graphs {#chapter-6}

## TL;DR {-}

At the end, your code will look like the following:

```{r 06.1-Complete-Code-Example, eval=FALSE}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1",
                  "Survey 2",
                  "Survey 3")

calculate_ind_trend_dem("Q1COVID19",
                        "gender",
                        df_list,
                        survey_dates,
                        "Algeria") |> 
  plot_ind_trend_dem(.caption = "Arab Barometer Wave VI, Algeria")


```


The code produces this graph:

```{r 06.2-Complete-Graph-Example, echo=FALSE, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1",
                  "Survey 2",
                  "Survey 3")

calculate_ind_trend_dem("Q1COVID19",
                        "gender",
                        df_list,
                        survey_dates,
                        "Algeria") |> 
  plot_ind_trend_dem(.caption = "Arab Barometer Wave VI, Algeria")


```

Hopefully you notice how similar this code is to the code in [Chapter 5](#chapter-5). The only difference here is that the user must include a line specifying the demographic.

## Prep Work {#chapter-6-1-1}

The prep work for creating a demographic trend graph for a single country is _exactly_ the same as the [prep work suggested for creating a trend graph for a single country](#chapter-5-1-1).

### Create a Data Frame List {- #chp6-trend-df-list}

The first step is to create a list of data frames. This section is exactly the same as the one from [here](#chp5-trend-df-list).

There should be one data frame for each period you wish to graph. That is, each data frame should be from a different survey you want to include in your graph. In the example for the chapter, we're using the three surveys from Wave VI, which we call `survey1`, `survey2`, and `survey3`. Each survey is its own data frame.

```{r 06.3-Single-Trend,echo=T,eval=FALSE}

df_list <- list(
  survey1,
  survey2,
  survey3
)

```


The list of data frames should be in the order you want them to appear (ideally, chronologically). The data on the graph will show up in the order of the list. So if you create a list in the order `list(survey2, survey1, survey3)`, the data from `survey2` will show up before the data from `survey1`. 

**Please note: This is ambivalent to language!** The `plot_ind_trend_dem()` function will assume the order of the list is the correct order, and treat it accordingly. When you enter a list as `list(survey1, survey2, surveye3)`, the English graph will show the data right to left (survey 1 -> survey 2 -> survey 3), while the Arabic graph will show the data left to right (survey 3 <- survey 2 <- survey 1). You do **not** need to alter your input.

> The data frame lists in the `Wave8TrendData` package do this step for you.

### Create a Date Vector {- #chp6-trend-date-vector}

This section is exactly the same as the one from [here](#chp5-trend-date-vector).

The next step is to create a vector of the dates you want to show on the x-axis of your graph. Branding guidelines call for the years in which the survey took place. For simplicity in the example, let's just say `"Survey X Year"`. 

You need a date for each data frame in your data frame list. Otherwise, the function won't know how to label the x-axis.


```{r 06.4-Single-Trend,echo=T,eval=FALSE}

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

```

The dates should also be in the order you want them to appear. The dates should line up with the data frames. In the chapter example, the order of the data frames is survey 1, survey 2, survey 3. Therefore, the survey dates need to have the order survey 1 year, survey 2 year, survey 3 year.

**Please note: This is ambivalent to language!** Just as with the data frame list, the `plot_ind_trend_dem()` function will put the data in the correct order according to the language of the graph.

Now that we have defined our data frame list and survey dates, we can create our demographic trend plot.

> The date vectors in the `Wave8TrendData` package do this step for you.

## Create a Summary {#chapter-6-1-2}

To create a demographic trend summary for an individual country, use the `calculate_ind_trend_dem()` function.

This function takes a few more parameters, and in a different order, than the functions we have worked with so far. In total, there are *five* necessary parameters: `.var`, `.dem`, `data_frames`, `survey_dates`, and `select_country`. To see a complete list of parameters, including optional ones, use `?calculate_ind_trend_dem()` in your `R` console.

The parameter `.var` is the variable you want to plot. **It must have the same name in every data frame in the data frame list.** If the variable you want to plot is named `"Q101"` in one sure, but `"Q102"` in another, the function will not include `"Q102"` in the plot. Computers can do a lot but as of yet they cannot think critically, so the onus is on you.

> The trend data lists from the `Wave8TrendData` package ensure this is true for Wave VIII variables.

The parameter `.dem` is the demographic you want to see the variable trends for. Much like the `.var` parameter, **it must have the same name in every data frame in the data frame list.** If the demographic you want to plot is named `"gender"` in one sure, but `"GENDER"` in another, the function will break.

The parameter `data_frames` is a list of data frames. This is what we created [here](chp6-trend-df-list). 

The parameter `survey_dates` is a character vector of dates that will show up on the x-axis of the graph. This is what we created [here](chp6-trend-date-vector).

The parameter `select_country` is the name of the country you want to create the graph for.

Now let's fill it in.

```{r 06.5-First-Example, eval=FALSE}

calculate_ind_trend_dem(
  .var           = "Q1COVID19",    # Variable to graph
  .dem           = "gender",       # Demographic to see over time
  data_frames    = df_list,        # List of data frames
  survey_dates   = survey_dates,   # Vector of survey dates
  select_country = "Algeria"       # Country to graph
  )


```

The output should look like the following, with the `Survey` column labeled.

```{r 06.6-First-Example, echo=FALSE}
individual_demographic_trend_summary <- calculate_ind_trend_dem(
  "Q1COVID19",    
  "gender",
  df_list,        
  survey_dates,   
  "Algeria"       
  )


knitr::kable(
  individual_demographic_trend_summary,
  booktabs = TRUE,
  label = NA
)


```

We can see the resulting data frame has six rows; one for each demographic in each survey we are plotting. Let's save the output as an object so we can plot that object in the next section.

```{r 06.7-First-Example}
individual_demographic_trend_summary <- calculate_ind_trend_dem(
  "Q1COVID19",    
  "gender",
  df_list,        
  survey_dates,   
  "Algeria"       
  )

```

## Plot the Summary {#chapter-6-1-3}

The next step is to plot the summary we just created. To do that, we use the function `plot_ind_trend_dem()`.

This function only *requires* one argument: `ab_summary`. Like many other graphs, we'll want to add a bit later on. To see a complete list of parameters, including optional ones, use `?plot_ind_trend_dem()` in your `R` console. For now, let's see what happens when we just supply our summary we saved as `individual_demographic_trend_summary`.


```{r 06.8,collapse=TRUE,fig.dim=c(13,12)}

plot_ind_trend_dem(
  ab_summary = individual_demographic_trend_summary
)

```

Nearly there! What still needs to be changed?

The caption, of course! Just as in all the other `plot_` functions in the `ArabBarometR` package, you can change the caption using the `.caption` parameter.

```{r 06.8.5,collapse=TRUE,fig.dim=c(13,12)}

plot_ind_trend_dem(
  ab_summary = individual_demographic_trend_summary,
  .caption = "Arab Barometer Wave VI, Algeria"
)

```

Putting all the steps together, we have the code and graph we originally started with.


```{r 06.9-Complete-Code-Example, eval=FALSE}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1",
                  "Survey 2",
                  "Survey 3")

calculate_ind_trend_dem("Q1COVID19",
                        "gender",
                        df_list,
                        survey_dates,
                        "Algeria") |> 
  plot_ind_trend_dem(.caption = "Arab Barometer Wave VI, Algeria")



```


```{r 06.10-Complete-Code-Example, echo=FALSE, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1",
                  "Survey 2",
                  "Survey 3")

calculate_ind_trend_dem("Q1COVID19",
                        "gender",
                        df_list,
                        survey_dates,
                        "Algeria") |> 
  plot_ind_trend_dem(.caption = "Arab Barometer Wave VI, Algeria")



```


## Extras 

### Human Readable

If you just want to look at the summaries and not necessarily create a plot, the output of `calculate_ind_trend_dem()` might not be the easiest to understand from a glance. There is a parameter called `human_readable` that is designed to help with that.

By default, `human_readable` is set to `FALSE` and each row is unique to the survey-demographic. If `human_readable` is set to `TRUE`, each is unique to a survey and there are columns for each demographic.

```{r 06.11-human-readable-f, eval=FALSE}

calculate_ind_trend_dem(
  .var           = "Q1COVID19",    
  .dem           = "gender",       
  data_frames    = df_list,        
  survey_dates   = survey_dates,   
  select_country = "Algeria",
  human_readable = FALSE       # This is the default
  )


```

```{r 06.12-human-readable-f, echo=FALSE}
individual_demographic_trend_summary_f <- calculate_ind_trend_dem(
  "Q1COVID19",    
  "gender",
  df_list,        
  survey_dates,   
  "Algeria"       
  )

knitr::kable(
  individual_demographic_trend_summary_f,
  booktabs = TRUE,
  label = NA,
  caption = "Default setting with `human_readable = FALSE`."
)

```


```{r 06.13-human-readable-3, eval=FALSE}

calculate_ind_trend_dem(
  .var           = "Q1COVID19",    
  .dem           = "gender",       
  data_frames    = df_list,        
  survey_dates   = survey_dates,   
  select_country = "Algeria",
  human_readable = TRUE       # This is NOT the default
  )


```

```{r 06.14-human-readable-t, echo=FALSE}
individual_demographic_trend_summary_t <- calculate_ind_trend_dem(
  "Q1COVID19",    
  "gender",
  df_list,        
  survey_dates,   
  "Algeria" ,
  human_readable = T
  )

knitr::kable(
  individual_demographic_trend_summary_t,
  booktabs = TRUE,
  label = NA,
  caption = "Default setting with `human_readable = TRUE`."
)

```


The default is set to `FALSE` because that is the structure `plot_ind_trend_dem()` expects. If you set `human_readable` to `TRUE` and use that output in `plot_ind_trend_dem()`, you will get an error.

### Font Size

The font size default brand size is used for the graph text. You can learn how to change that in [the chapter on changing the font size](#change-font-size).

### Colors

You can learn how to change the colors for the single country trend graph in [the chapter on changing graph colors](#change-colors-trend-comparative).

