# (PART) Multiple Questions {-}

# Single Country Multi-Question Plots

This chapter teaches you how to create a single graph that summarizes responses for multiple variables for a single country. 

These types of graphs are especially useful for plotting **grid** questions. Grid questions use the same stem, but have different endings. Technically, while related, they are all unique questions. Therefore, plotting a set of grid questions on the same graph, is the same thing as plotting multiple question on one graph.

**All questions are required to be the same type when using this function.** Comparing the responses to different question types is not advised, so the function does not allow for it.

At the end, your code will look like the following:

```{r 09.1-Complete-Code-Example, eval=FALSE}

questions_2_compare <- list("Q210",
                            "Q211")
questions_labels <- c("Is there corruption?",
                      "Is the gov't cracking down?")

plot_multiquestions_ind(survey1,
                        questions_2_compare,
                        questions_labels,
                        "Algeria",
                        .title = "Perceptions of Corruption in Algeria",
                        .subtitle = "% saying to a medium or large extent",
                        .caption = "Arab Barometer Wave VI, Survey 1, Algeria")

```

That code will produce the following graph:


```{r 09.2-Complete-Graph-Example, echo=FALSE, fig.dim=c(13,12)}

questions_2_compare <- list("Q210",
                            "Q211")
questions_labels <- c("Is there corruption?",
                      "Is the gov't cracking down?")

plot_multiquestions_ind(survey1,
                        questions_2_compare,
                        questions_labels,
                        "Algeria",
                        .title = "Perceptions of Corruption in Algeria",
                        .subtitle = "% saying to a medium or large extent",
                        .caption = "Arab Barometer Wave VI, Survey 1, Algeria")
```

Let's go!

## Prep Work

There is no **calculate_** function^[As off writing this chapter] for this graph. All the computation is done within the `plot_multiquestions_ind()` function.

It is useful to do some prep work to keep everything clear.

### Question List

First create a list of questions you want to include on your graph. For the example in this chapter we are comparing questions `Q210` and `Q211`. We put the names of those variables in a list and save that list as an object.

```{r 09.3-question-list}

questions_2_compare <- list(
  "Q210",
  "Q211"
  )

```

Now the variables we want to graph as saved to the object `questions_2_compare` in a list.

### Question Labels

The next step is to create a vector of labels for the questions. This is the text that will display on the y-axis. The labels should appear in the same order as they variables they are referring to.

```{r 09.4-question-labels}

question_labels <- c(
  "Is there corruption?",       # Text for Q210
  "Is the gov't cracking down?" # Text for Q211
  )

```

The object `question_labels` represents the text that will serve to label the responses on the graph.

## Plot a Multiquestion Graph for a Single Country

We are now ready to create our graph. The function `plot_multiquestions_ind()` is used to create a graph for one country that displays responses to multiple questions. There are **three** required arguments. They are: `.ab`, `.questions`, and `.question_labels`.

The parameter `.ab` is the for Arab Barometer data frame. If there is only one country in the data, the function will automatically know which country it is^[As long as the data frame is a standard Arab Barometer data frame containing a `COUNTRY` column.]. If there is more than one country in the data set, you __must__ use the `.country` parameter to specify which country you want to graph.

The `.questions` parameter requires a list (or vector) of questions. This is how the function knows which questions to include on the graph. We created a list, `questions_2_compare`, in the section above.

The `.question_labels` parameter requires a vector (or list) of question labels. The labels must appear in the same order as the questions to appear on the graph correctly. We created a vector, `questions_labels`, in the section above.

Time to fill in our function. The data we are using for the example is `survey1`. This data frame includes all the countries surveyed during the first round of surveys in Wave VI. We must use the `.country` parameter to tell the function which country we wish to plot.

```{r 09.5-first-graph,fig.dim=c(13,12)}

plot_multiquestions_ind(
  .ab = survey1,
  .questions = questions_2_compare,
  .question_labels = question_labels,
  .country = "Algeria"
)

```

Notice there are several missing elements in this graph. Namely, an appropriate title, subtitle, and caption. These three aspects are not included in the list of *required* arguments, because a graph can be created without them. If you want to use the graph publicly, however, it would be prudent to include them.

The parameters for including a title, subtitle, and caption are the same as they are in any other function: `.title`, `.subtitle`, and `.caption`, respectively. We can fill these in to create our final graph.

```{r 09.6-second-graph}

plot_multiquestions_ind(
  .ab = survey1,
  .questions = questions_2_compare,
  .question_labels = question_labels,
  .country = "Algeria",
  .title = "Perceptions of Corruption in Algeria",
  .subtitle = "% saying to a medium or large extent",
  .caption = "Arab Barometer Wave VI, Survey 1, Algeria"
)

```

## Extras

### Setting Colors

By default, the colors for the graph are randomly selected from `ArabBarometer_clr`. To set the colors of the graph, supply a vector of hex codes or named Arab Barometer brand colors to the parameter `.clr_choice`.

### Data Frame

There is no **calculate_** function that accompanies this function. All calculations are done internally. The parameter `.return_df` allows the user to see the data frame used to create the graph. Setting `.return_df` to `TRUE` will cause the function to return a list containing the graph and the data frame. Setting `.return_df` to `"only"` will cause the function to only return the data frame.

### Explict Grid Example

Remember: plotting a set of grid questions requires exactly the same steps as outlined throughout this chapter. There is **no difference** between plotting 2 (or n) questions that belong to a grid, and 2 (or n) questions that do not.

```{r}

# Identifying two question from a grid set:
questions_2_compare <- list(
  "Q201A_1",
  "Q201A_2"
)

# Supplying labels:
question_labels <- c(
  "Government",
  "Legal system"
)

# Plotting the grid questions:
plot_multiquestions_ind(
  .ab = survey1,
  .questions = questions_2_compare,
  .question_labels = question_labels,
  .country = "Algeria",
  .title = "How much trust do you have in...",
  .subtitle = "% of Algerians saying they have quite a lot or a great deal",
  .caption = "Arab Barometer Wave VI, Survey 1, Algeria"
)

```

