# Comparative Multi-Question Plots {#chapter-10}

This chapter teaches you how to create a single graph that summarizes responses for multiple variables for many countries. 

These types of graphs are especially useful for plotting **grid** questions. Grid questions use the same stem, but have different endings. Technically, while related, they are all unique questions. Therefore, plotting a set of grid questions on the same graph, is the same thing as plotting multiple question on one graph.

**All questions are required to be the same type when using this function.** Comparing the responses to different question types is not advised, so the function does not allow for it.

### TL;DR {-}

At the end, your code will look like the following:

```{r 10.1-Complete-Code-Example, eval=FALSE}

questions_2_compare <- list("Q210",
                            "Q211")

question_labels <- c("Is there corruption?",
                      "Is the gov't cracking down?")

calculate_comp_multiq_smry(survey1,
                           questions_2_compare,
                           question_labels) |> 
  plot_comp_multiq_smry(.title = "Perceptions of Corruption in MENA",
                           .subtitle = "% saying to a medium or large extent",
                           .caption = "Arab Barometer Wave VI, Survey 1")

```

That code will produce the following graph:


```{r 10.2-Complete-Graph-Example, echo=FALSE, fig.dim=c(13,12)}

questions_2_compare <- list("Q210",
                            "Q211")

question_labels <- c("Is there corruption?",
                      "Is the gov't cracking down?")

calculate_comp_multiq_smry(survey1,
                           questions_2_compare,
                           question_labels) |> 
  plot_comp_multiq_smry(.title = "Perceptions of Corruption in MENA",
                           .subtitle = "% saying to a medium or large extent",
                           .caption = "Arab Barometer Wave VI, Survey 1")

```

Let's go!

## Prep Work {#chapter-10-1}

The prep work for creating a multiquestion graph for many countries is _exactly_ the same as the [prep work suggested for creating a multiquesiton graph for a single country](#new-chapter-9-1).

### Question List {#chapter-10-1-1}

First create a list of questions you want to include on your graph. For the example in this chapter we are comparing questions `Q210` and `Q211`. We put the names of those variables in a list and save that list as an object.

```{r 10.3-question-list}

questions_2_compare <- list(
  "Q210",
  "Q211"
  )

```

Now the variables we want to graph as saved to the object `questions_2_compare` in a list.

### Question Labels {#chapter-10-1-2}

The next step is to create a vector of labels for the questions. This is the text that will display on the y-axis. The labels should appear in the same order as they variables they are referring to.

```{r 10.4-question-labels}

question_labels <- c(
  "Is there corruption?",       # Text for Q210
  "Is the gov't cracking down?" # Text for Q211
  )

```

The object `question_labels` represents the text that will serve to label the responses on the graph.

## Create a Summary {#chapter-10-2}

Now we create our summary. The function `calculate_comp_multiq_smry()` is used to create a summary for multiple countries that displays responses to multiple questions. There are **three** required arguments. They are: `.ab`, `.questions`, and `.question_labels`.

The parameter `.ab` is the for Arab Barometer data frame.

The `.questions` parameter requires a vector of questions. This is how the function knows which questions to include on the graph. We created a list, `questions_2_compare`, in the section above.

The `.question_labels` parameter requires a vector of question labels. The labels must appear in the same order as the questions to appear on the graph correctly. We created a vector, `questions_labels`, in the section above.

Time to fill in our function. The data we are using for the example is `survey1`.

```{r 10.5-first-summary}

calculate_comp_multiq_smry(
  .ab = survey1,
  .questions = questions_2_compare,
  .question_labels = question_labels
)

```

Notice that the column `"Question"` is labeled. This is where the labels in our legend will come from.

Let's save the output to an object we can feed to our plotting function in the next section.

```{r 10.6-second-summary}

comp_multiq_smry <- calculate_comp_multiq_smry(
  survey1,
  questions_2_compare,
  question_labels
)

```


## Plot a Comparative Multiquestion Graph {#chapter-10-3}

Next we use the function `plot_comp_multiq_smry()` to create a plot of our summary. The function only requires one parameter, `ab_summary`. We will use the summary we created above and saved to the object `comp_multiq_smry`.

```{r 10.7-first-graph,fig.dim=c(13,12)}

plot_comp_multiq_smry(
  ab_summary = comp_multiq_smry
)

```

Notice there are several missing elements in this graph. Namely, an appropriate title, subtitle, and caption. These three aspects are not included in the list of *required* arguments, because a graph can be created without them. If you want to use the graph publicly, however, it would be prudent to include them.

You may notice the warnings as well. Some warnings are telling you a graph was made, but there is no title or subtitle. These will go away once we provide a title and subtitle. You can read more about these warnings in the section [How do I Understand (some) Messages, Warnings, and Errors](#standard-warnings). The rest of the chapter supresses the warnings.

The parameters for including a title, subtitle, and caption are the same as they are in any other function: `.title`, `.subtitle`, and `.caption`, respectively. We can fill these in to create our final graph.

```{r 10.6-second-graph, fig.dim=c(13,12), warning=FALSE}

plot_comp_multiq_smry(
  ab_summary = comp_multiq_smry,
  .title = "Perceptions of Corruption in MENA",
  .subtitle = "% saying to a medium or large extent",
  .caption = "Arab Barometer Wave VI, Survey 1"
)

```

## Extras {#chapter-10-4}

### Setting Colors {#chapter-10-4-1}

By default, the colors for the graph are randomly selected from `ArabBarometer_clr`. To set the colors of the graph, supply a vector of hex codes or named Arab Barometer brand colors to the parameter `.color_choice`.

### Select Countries {#chapter-10-4-2}

By default, all the countries in the data frame you pass to the calculate function are included in the summary. You can filter these countries with the `.select_countries` parameter. You can learn more about the `.select_countries` filter in the section [How do I Show Only Certain Countries?](#select-countries-chp)

### Explict Grid Example {#chapter-10-4-3}

Remember: plotting a set of grid questions requires exactly the same steps as outlined throughout this chapter. There is **no difference** between plotting 2 (or n) questions that belong to a grid, and 2 (or n) questions that do not.

```{r 10.7-grid-example, fig.dim=c(13,12), warning=FALSE}

# Identifying two question from a grid set:
questions_2_compare <- list(
  "Q201A_1",
  "Q201A_2"
)

# Supplying labels:
question_labels <- c(
  "Government",
  "Legal system"
)

# Plotting the grid questions:
calculate_comp_multiq_smry(survey1,
                           questions_2_compare,
                           question_labels) |> 
  plot_comp_multiq_smry(.title = "How much trust do you have in...",
                        .subtitle = "% saying they have quite a lot or a great deal",
                        .caption = "Arab Barometer Wave VI, Survey 1")

```


### Warnings {#chapter-10-warnings}

There are several points in this code when warnings or messages will appear **even if you are using the code correctly.** No need to panic. You can read about all of the messages and warnings that may appear *even when the code is correct* in the section [How do I Understand (some) Messages, Warnings, and Errors](#standard-warnings).

The function `plot_comp_multiq_smry()` will produce a `position_dodge()` warning. You can read a bit about that [here](#warning-dodge).

If you do not supply a title or subtitle, a plot will still be created but you will receive a missing title and/or subtitle warning. You can read more about this [here](#warning-title).