# Change Default Colors {#change-colors}


## Basic Cross Tabs {#change-colors-basic}

The parameter is called **`.color_choice`**. This parameter accepts either a color name from `ArabBarometR` or a hex code.

```{r How.3.1-Complete-Code-Example, fig.dim=c(13,12)}

survey1  |> 
  calculate_smry_individual("Q1COVID19",
                            "Algeria") |>
  plot_smry_individual(.color_choice = "zeke")

survey1 |>
  calculate_smry_comp("Q1COVID19") |>
  plot_smry_comp(.color_choice = "#FF5E64")


```


## Demographic Cross Tabs {#change-colors-demographic}

The parameter to change is called **`.color_choice`**. This parameter accepts any of the following:

  * `"default"` (which it is set to),
  * the name of an `ArabBarometR` color palette,
  * a vector of `ArabBarometR` color names, or
  * a vector of hex codes.
  
If you choose to use a vector of either color names or hex codes, it **must** be the same length as the number of demographic categories. For example, the `gender` demographic has two categories, so a vector of custom colors needs to be length two. You can check the number of categories by looking at the data frame you are plotting.

```{r How.3.2-Complete-Code-Example, fig.dim=c(13,12),warning=FALSE}

survey1 |>
  calculate_demographic_smry_individual("Q1COVID19",
                                        "Algeria",
                                        .dem = "gender") |> 
  plot_demographic_smry_individual(.color_choice = "blue pair")

survey1 |>
  calculate_demographic_smry_comp("Q1COVID19",
                                  .dem = "gender") |> 
  plot_demographic_smry_comp(.color_choice = c("salma","mary clare"))

data_frame_2_plot <- survey1 |>
  calculate_demographic_smry_comp("Q1COVID19",
                                  .dem = "Q101") 

data_frame_2_plot


# 6 categories means 6 colors needed
data_frame_2_plot |> 
  plot_demographic_smry_comp(.color_choice = c("#0098BE",
                                                         "#DF6E21",
                                                         "#AC517F",
                                                         "#7CBBC7",
                                                         "#796391",
                                                         "#CF83A3"))


```


## Stacked Graphs {#change-colors-stacked}

The parameter is called **`.color_choice`**. The parameter accepts any of the following:

  * the name of an `ArabBarometR` color palette,
  * a vector of `ArabBarometR` color names, or
  * a vector of hex codes.
  
If you choose to use a vector of either color names or hex codes, it **must** be the same length as the number of categories. Recall that the categories "don't know" and "refuse" are combined into a single category unless otherwise specified. When determining the number of colors you need for your vector, only count the "don't know" and "refuse" categories as one category.

Take `Q2061A` as an example. In the first survey of wave six, question `Q2061A` had ten response options including "don't know" and "refuse". The `calculate_stacked_df()` function combines "don't konw" and "refuse" into one category, so the color palette vector only needs to be length nine.

```{r How.3.3-Complete-Code-Example, fig.dim=c(13,12),warning=FALSE}

calculate_stacked_df(survey1,
                     "Q2061A") |>
  plot_stacked_comp(.caption = "Arab Barometer Wave VI, Survey 1",
                    .color_choice = "soft rainbow")

calculate_stacked_df(survey1,
                     "Q2061A") |>
  plot_stacked_comp(.caption = "Arab Barometer Wave VI, Survey 1",
                    .color_choice = c("AB blue",
                                       "AB orange",
                                       "AB magenta",
                                       "AB light blue",
                                       "AB purple",
                                       "AB pink",
                                       "AB yellow",
                                       "zeke",
                                       "pale green"))


```

## Trend Graphs {#change-colors-trend}

By default trend graphs are created in the brand color assigned to them. If you wish to change the color, you can do so by setting the parameter `.color_choice` to either a hex code or a color from `ArabBarometer_colors()`.

### Single Country Trend Graphs {- #change-colors-trend-single}

Changing the color for single country trend graphs is exactly the same as for [basic cross tabs](#change-colors-basic), only using a different parameter name.

```{r How.3.4-Complete-Code-Example, fig.dim=c(13,12),eval=FALSE}


plot_trend_individual("Q1COVID19",
                      df_list,
                      survey_dates,
                      "Algeria",
                      .caption = "Arab Barometer Wave VI, Algeria",
                      .color_choice = "bright apple")  # Arab Barometer color name

plot_trend_individual("Q1COVID19",
                      df_list,
                      survey_dates,
                      "Algeria",
                      .caption = "Arab Barometer Wave VI, Algeria",
                      .color_choice = "#C8C6A2") # hex code

```

### Comparative Trend Graphs {- #change-colors-trend-comparative}

There is greater flexibility in colors for comparative trend graphs. The user may supply a named or unnamed vector of hex codes or Arab Barometer brand colors. 


```{r How.3.5-Complete-Code-Example, fig.dim=c(13,12),warning=FALSE,eval=FALSE}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1",
                  "Survey 2",
                  "Survey 3")

# Unnamed color example
plot_trend_comp("Q1COVID19",
                df_list,
                survey_dates,
                .caption = "Arab Barometer Wave VI",
                select_countries = c("Lebanon","Morocco"),
                .color_choice = c("bright apple","james bond")
)


# Named color example
trend_colors <- c("bright apple","james bond")
names(trend_colors) <- c("Morocco","Lebanon")


plot_trend_comp("Q1COVID19",
                df_list,
                survey_dates,
                .caption = "Arab Barometer Wave VI",
                select_countries = c("Morocco","Lebanon"),
                .color_choice = trend_colors
)
```

The user can also change the color of some but not all countries.

```{r How.3.6-Complete-Code-Example, fig.dim=c(13,12),warning=FALSE,eval=FALSE}
# Change one color example
plot_trend_comp("Q1COVID19",
                df_list,
                survey_dates,
                .caption = "Arab Barometer Wave VI",
                select_countries = c("Morocco","Lebanon"),
                .color_choice = c("Lebanon" = "#C8C6A2") 
) 


```
