# Show only certain countries? {#select-countries-chp}

To choose only certain countries to plot, use the parameter `select_countries`. If you are creating a plot with a `calculate_` function, this parameter is in `calculate_` function. If the plot only uses the `plot_` function, this parameter is in the `plot_` function. The parameters is called `select_countries` in both cases.

## Plots that go with `calculate_` functions {#select-countries-calculate}


```{r How.5.6.1-SelectCountries, fig.dim=c(13,12)}

survey1 %>%
  calculate_smry_comp("Q1COVID19",
                      select_countries = c("Morocco","Tunisia")) %>%
  
  plot_smry_comp(.caption = "Arab Barometer Wave VI, Survey I")


```

## Plots with no `calculate_` functions {#select-countries-no-calculate}

```{r How.5.7.1-SelectCountries, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1",
                  "Suvey 2",
                  "Survey 3")


plot_trend_comp("Q1COVID19",
                df_list,
                survey_dates,
                select_countries = c("Morocco",
                                     "Lebanon"))

```
