# Change the order of a stacked graph?

Changing the order of a stacked graph, like creating many graphs at once, is not done within `ArabBarometR` per se, but the process is relatively straightforward nonetheless.

For this example, let's create a comparative stacked bar chart for `Q2ACOVID19`.

```{r How.4.01-Complete-Code-Example,fig.dim=c(13,12)}

calculate_stacked_df(survey1,
                     "Q2ACOVID19") %>%
  plot_stacked_comp(.caption = "Original Order")


```

The order of the bars is determined by the factor level. You can see factor level in the data frame produced by the function `calculate_stacked_df`. The numbers are the factor levels, the words in brackets are the factor labels. In this example, you can see the factor levels are 1-7 and 666. The factor labels are the question response options.


```{r How.04.2-og.factor.look}

calculate_stacked_df(survey1,
                     "Q2ACOVID19")


```


Instead of leading with "Illness or death of a family member", say we want to lead with "Inadequate gov.t response". We need to change the factor levels. First, we'll save the output of `calculate_stacked_df` to an object we can manipulate.


```{r How.04.2-SaveOutput}

new_df <- calculate_stacked_df(survey1,
                               "Q2ACOVID19")


```
 
To change the factor levels, we'll use the `recode` function from the `dplyr` library. There are several ways you can use the `recode` function to re-order the factor levels. This guide will review two, and you can explore the rest on your own.

### Move One Factor {-}

If the goal is to move "Inadequate gov.t response", whose factor level is `5`, in front of "Illness or death of a family member", whose factor level is `1`, we have to choose a new factor level that comes before `1`. There are infinite numbers before `1`, so we'll just go with `0.5` here.

```{r How.04.2-recode1}

new_df$Q2ACOVID19 <- dplyr::recode(
  new_df$Q2ACOVID19,                     # The variable getting recoded
  `5` = .5,                              # The old value to new value
  .default = levels(new_df$Q2ACOVID19),  # Use the original levels as a guide
  .combine_value_labels = T              # Keep the original levels for all other variables
  )


```

We can see the new value of the factor.

```{r How.04.2-recoded1output,echo=FALSE}

new_df

```

And now when we plot the recoded data frame.


```{r How.04.2-PlotRecode1,fig.dim=c(13,12)}

new_df %>%
  plot_stacked_comp(.caption = "New Order, Option 1")

```

### Swap Factors {-}

An alternative way to move "Inadequate gov.t response" to the front is to swap positions with "Illness or death of a family member". That is, make "Inadequate gov.t response" factor level `1` and "Illness or death of a family member" factor level `5`. Again, we use `recode` from `dplyr`.


```{r How.04.2-SaveOutput2,echo=FALSE}

new_df <- calculate_stacked_df(survey1,
                               "Q2ACOVID19")


```

```{r How.04.2-recode2}

new_df$Q2ACOVID19 <- dplyr::recode(
  new_df$Q2ACOVID19,                     # The variable getting recoded
  `5` = 1,                               # The old value to new value
  `1` = 5,                               # The old value to new value
  .default = levels(new_df$Q2ACOVID19),  # Use the original levels as a guide
  .combine_value_labels = T              # Keep the original levels for all other variables
  )


```

The new factor levels are:


```{r How.04.2-recoded2output,echo=FALSE}

new_df

```

Finally, we plot the new data frame.

```{r How.04.2-PlotRecode2,fig.dim=c(13,12)}

new_df %>%
  plot_stacked_comp(.caption = "New Order, Option 2")

```

The main take away here is that if you want to play around with the order of a stacked bar graph, it is best to familiarize yourself with `recode`.