
## Create Many Graphs {#chapter-5-2}

A nice payoff of creating the [data frame list](#chp5-trend-df-list) and the [date vector](#chp5-trend-date-vector) is that these objects (`df_list` and `survey_dates`) can be re-used any time you want to create a graph over the same time period. 

For example, say you wanted to also create a graph tracking Algerian's views of the economy and religiosity. The only parameter in the `plot_trend_individual()` function that needs updating is `.var`.


```{r 05.10-Many-Graphs-Example1, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

plot_trend_individual("Q1COVID19",
                      df_list,
                      survey_dates,
                      "Algeria",
                      .caption = "Arab Barometer Wave VI, Algeria")

plot_trend_individual("Q101",
                      df_list,
                      survey_dates,
                      "Algeria",
                      .caption = "Arab Barometer Wave VI, Algeria")

plot_trend_individual("Q609",
                      df_list,
                      survey_dates,
                      "Algeria",
                      .caption = "Arab Barometer Wave VI, Algeria")
 

```

Notice that the code produced two graphs, even though `df_list` and `survey_dates` were only defined one time. Once you have created the `df_list` and `survey_dates` objects, you can re-use them for any graph that is covering the same time period.

You can also you the `map()` function from the `purrr` package. This method is similar to what was done for creating [many single country graphs](#plot-many-graphs-single-country), [many single country demographic graphs](plot-many-graphs-single-country-demographic), [many comparative graphs](#plot-many-comparative), and [many comparative demographic graphs](#plot-many-comparative-demographic).

As a quick review, in earlier chapters the first step was identify the variables to plot. We did that by creating a named list of of the variables we wanted to plot.

The second step was creating a list of summaries by give the summarize function the named variable list. 

The third and final step was mapping that list of summaries to the related plot function. In the mapping function, we would hold the caption constant since we wanted the same caption to appear on every graph.

The `plot_trend_individual()` function creates summaries internally, so we can "skip" the second step. Once we identify our variables, we go right to the mapping step. We map a named list of variables to the `plot_trend_individual()` function. We want to create a graph for the same country over the same time period, just using different variable, so we hold the data frame list, survey dates, country, *and* caption constant.

### Identify the Variables {#chapter-5-2-1}

We are creating trend graphs for the variables `Q1COVID19`, `Q101`, and `Q609`. 

```{r 05.11-Many-Graphs-Example2, fig.dim=c(13,12)}

variables_2_plot <- list("Q1COVID19",
                         "Q101",
                         "Q609")

names(variables_2_plot) <- c("Q1COVID19",
                             "Q101",
                             "Q609")

```

Now you have a names list of variables. Let's plot them.

### Plot the Variables {#chapter-5-2-2}

Recall we want to hold constant the `data_frames`, `survey_dates`, `select_country` and `.caption` parameters because those will be the same for every graph. The only parameter we want to vary is `.var`.

```{r 05.12-Many-Graphs-Example2, fig.dim=c(13,12)}

plots <- map(
  variables_2_plot, # Vector of variables to plot
  plot_trend_individual, # Map to function `plot_trend_individual()`
  
  data_frames    = df_list,  # Hold constant the `data_frames` parameter
  survey_dates     = survey_dates, # Hold constant the `survey_dates` parameter
  select_country = "Algeria", # Hold constant the `select_country` parameter
  .caption       = "Arab Barometer Wave VI, Algeria"
  )

```

Excellent!

The plots have been saved to a named list called `plots`. To access the plots for each variable, you can use the `$` and variable name.

```{r 05.13-Many-Graphs-Example2, fig.dim=c(13,12)}

# Trend graph for Q1COVID19
plots$Q1COVID19

# Trend graph for Q101
plots$Q101

# Trend graph for Q609
plots$Q609

```

You've done it! You have created many trend plots at once!


## Create Many Graphs {#chapter-6-2}

A nice payoff of creating the [data frame list](#chp6-trend-df-list) and the [date vector](#chp6-trend-date-vector) is that these objects (`df_list` and `survey_dates`) can be re-used any time you want to create a graph over the same time period. 

For example, say you wanted to also create a graph tracking Algerian's views of the economy and religiosity. The only parameter in the `plot_trend_individual_demographics()` function that needs updating is `.var`.


```{r 06.11-Many-Graphs-Example1, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

plot_trend_individual_demographics("Q1COVID19",
                                   "gender",
                                   df_list,
                                   survey_dates,
                                   "Algeria",
                                   .caption = "Arab Barometer Wave VI, Algeria")

plot_trend_individual_demographics("Q101",
                                   "gender",
                                   df_list,
                                   survey_dates,
                                   "Algeria",
                                   .caption = "Arab Barometer Wave VI, Algeria")

plot_trend_individual_demographics("Q609",
                                   "gender",
                                   df_list,
                                   survey_dates,
                                   "Algeria",
                                   .caption = "Arab Barometer Wave VI, Algeria")
 

```

Notice that the code produced two graphs, even though `df_list` and `survey_dates` were only defined one time. Once you have created the `df_list` and `survey_dates` objects, you can re-use them for any graph that is covering the same time period.

You can also you the `map()` function from the `purrr` package. This method is similar to what was done for creating [many single country graphs](#plot-many-graphs-single-country), [many single country demographic graphs](plot-many-graphs-single-country-demographic), [many comparative graphs](#plot-many-comparative), and [many comparative demographic graphs](#plot-many-comparative-demographic).

As a quick review, in earlier chapters the first step was identify the variables to plot. We did that by creating a named list of of the variables we wanted to plot.

The second step was creating a list of summaries by give the summarize function the named variable list. 

The third and final step was mapping that list of summaries to the related plot function. In the mapping function, we would hold the caption constant since we wanted the same caption to appear on every graph.

The `plot_trend_individual_demographics()` function creates summaries internally, so we can "skip" the second step. Once we identify our variables, we go right to the mapping step. We map a named list of variables to the `plot_trend_individual_demographics()` function. We want to create a graph for the same country over the same time period, just using different variable, so we hold the demographic, data frame list, survey dates, country, *and* caption constant.

### Identify the Variables {#chapter-6-2-1}

We are creating trend graphs for the variables `Q1COVID19`, `Q101`, and `Q609`. 

```{r 06.12-Many-Graphs-Example2, fig.dim=c(13,12)}

variables_2_plot <- list("Q1COVID19",
                         "Q101",
                         "Q609")

names(variables_2_plot) <- c("Q1COVID19",
                             "Q101",
                             "Q609")

```

Now you have a names list of variables. Let's plot them.

### Plot the Variables {#chapter-6-2-2}

Recall we want to hold constant the `data_frames`, `survey_dates`, `select_country` and `.caption` parameters because those will be the same for every graph. The only parameter we want to vary is `.var`.

```{r 06.13-Many-Graphs-Example2, fig.dim=c(13,12)}

plots <- map(
  variables_2_plot, # Vector of variables to plot
  plot_trend_individual_demographics, # Map to function `plot_trend_individual_demographics()`
  
  .dem           = "gender", # Hold constant the `.dem` parameter
  data_frames    = df_list,  # Hold constant the `data_frames` parameter
  survey_dates     = survey_dates, # Hold constant the `survey_dates` parameter
  select_country = "Algeria", # Hold constant the `select_country` parameter
  .caption       = "Arab Barometer Wave VI, Algeria"
  )

```

Excellent!

The plots have been saved to a named list called `plots`. To access the plots for each variable, you can use the `$` and variable name.

```{r 06.14-Many-Graphs-Example2, fig.dim=c(13,12)}

# Trend graph for Q1COVID19
plots$Q1COVID19

# Trend graph for Q101
plots$Q101

# Trend graph for Q609
plots$Q609

```

You've done it! You have created many trend plots at once!

## Create Many Graphs {#chapter-7-2}

A nice payoff of creating the [data frame list](#chp7-trend-df-list) and the [date vector](#chp7-trend-date-vector) is that these objects (`df_list` and `survey_dates`) can be re-used any time you want to create a graph over the same time period. 

For example, say you wanted to also create a graph tracking the region's views of the economy and religiosity. The only parameter in the `plot_trend_comp()` function that needs updating is `.var`.


```{r 07.10-Many-Graphs-Example1, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

plot_trend_comp("Q1COVID19",
                df_list,
                survey_dates,
                .caption = "Arab Barometer Wave VI")

plot_trend_comp("Q101",
                df_list,
                survey_dates,
                .caption = "Arab Barometer Wave VI")

plot_trend_comp("Q609",
                df_list,
                survey_dates,
                .caption = "Arab Barometer Wave VI")
 

```

Notice that the code produced two graphs, even though `df_list` and `survey_dates` were only defined one time. Once you have created the `df_list` and `survey_dates` objects, you can re-use them for any graph that is covering the same time period.

You can also you the `map()` function from the `purrr` package. This method is similar to what was done for creating [many single country graphs](#plot-many-graphs-single-country), [many single country demographic graphs](plot-many-graphs-single-country-demographic), [many comparative graphs](#plot-many-comparative), and [many comparative demographic graphs](#plot-many-comparative-demographic).

As a quick review, in earlier chapters the first step was identify the variables to plot. We did that by creating a named list of of the variables we wanted to plot.

The second step was creating a list of summaries by give the summarize function the named variable list. 

The third and final step was mapping that list of summaries to the related plot function. In the mapping function, we would hold the caption constant since we wanted the same caption to appear on every graph.

The `plot_trend_comp()` function creates summaries internally, so we can "skip" the second step. Once we identify our variables, we go right to the mapping step. We map a named list of variables to the `plot_trend_comp()` function. We want to create a graph for all countries over the same time period, just using different variable, so we hold the data frame list, survey dates, *and* caption constant.

### Identify the Variables {#chapter-7-2-1}

We are creating trend graphs for the variables `Q1COVID19`, `Q101`, and `Q609`. 

```{r 07.11-Many-Graphs-Example2, fig.dim=c(13,12)}

variables_2_plot <- list("Q1COVID19",
                         "Q101",
                         "Q609")

names(variables_2_plot) <- c("Q1COVID19",
                             "Q101",
                             "Q609")

```

Now you have a names list of variables. Let's plot them.

### Plot the Variables {#chapter-7-2-2}

Recall we want to hold constant the `data_frames`, `svry_dates`, and `.caption` parameters because those will be the same for every graph. The only parameter we want to vary is `.var`.

```{r 07.12-Many-Graphs-Example2, fig.dim=c(13,12)}

plots <- map(
  variables_2_plot, # Vector of variables to plot
  plot_trend_comp, # Map to function `plot_trend_comp()`
  
  data_frames    = df_list,  # Hold constant the `data_frames` parameter
  svry_dates     = survey_dates, # Hold constant the `svry_dates` parameter
  .caption       = "Arab Barometer Wave VI"
  )

```

Excellent!

The plots have been saved to a named list called `plots`. To access the plots for each variable, you can use the `$` and variable name.

```{r 07.13-Many-Graphs-Example2, fig.dim=c(13,12)}

# Trend graph for Q1COVID19
plots$Q1COVID19

# Trend graph for Q101
plots$Q101

# Trend graph for Q609
plots$Q609

```

You've done it! You have created many trend plots at once!

## Create Many Graphs

On a rare occasion, it is conceivable that you might want to create many comparative demographic trend graphs for a slew of variables. For the sake of simplicity, let's assume you all the graphs to be displayed the same way and set the `.facet_choice` parameter to `"Country"` for the example.

A nice payoff of creating the [data frame list](#chp8-trend-df-list) and the [date vector](#chp8-trend-date-vector) is that these objects (`df_list` and `survey_dates`) can be re-used any time you want to create a graph over the same time period. 

For example, say you wanted to also create a graph tracking Algerian's views of the economy and religiosity. The only parameter in the `plot_trend_comp_demographics()` function that needs updating is `.var`.


```{r 08.18-Many-Graphs-Example1, fig.dim=c(13,12)}

df_list <- list(
  survey1,
  survey2,
  survey3
)

survey_dates <- c("Survey 1 Year",
                  "Survey 2 Year",
                  "Survey 3 Year")

plot_trend_comp_demographics("Q1COVID19",
                             "gender",
                             df_list,
                             survey_dates,
                             "Country",
                             .caption = "Arab Barometer Wave VI")

plot_trend_comp_demographics("Q101",
                             "gender",
                             df_list,
                             survey_dates,
                             "Country",
                             .caption = "Arab Barometer Wave VI")

plot_trend_comp_demographics("Q609",
                             "gender",
                             df_list,
                             survey_dates,
                             "Country",
                             .caption = "Arab Barometer Wave VI")
 

```

Notice that the code produced two graphs, even though `df_list` and `survey_dates` were only defined one time. Once you have created the `df_list` and `survey_dates` objects, you can re-use them for any graph that is covering the same time period.

You can also you the `map()` function from the `purrr` package. This method is essentially the same as what was done for [creating many single country demographic trend graphs](#chapter6-2).

As a quick review, in earlier chapters the first step was identify the variables to plot. We did that by creating a named list of of the variables we wanted to plot.

The `plot_trend_comp_demographics()` function creates summaries internally, so once we identify our variables, we go right to the mapping step. We map a named list of variables to the `plot_trend_comp_demographics()` function. We want to create a graph for the same country over the same time period, just using different variable, so we hold the demographic, data frame list, survey dates, facet choice, *and* caption constant.

### Identify the Variables

We are creating trend graphs for the variables `Q1COVID19`, `Q101`, and `Q609`. 

```{r 08.19-Many-Graphs-Example2, fig.dim=c(13,12)}

variables_2_plot <- list("Q1COVID19",
                         "Q101",
                         "Q609")

names(variables_2_plot) <- c("Q1COVID19",
                             "Q101",
                             "Q609")

```

Now you have a names list of variables. Let's plot them.

### Plot the Variables

Recall we want to hold constant the `data_frames`, `svry_dates`, `.facet_choice` and `.caption` parameters because those will be the same for every graph. The only parameter we want to vary is `.var`.

```{r 08.20-Many-Graphs-Example2, fig.dim=c(13,12)}

plots <- map(
  variables_2_plot, # Vector of variables to plot
  plot_trend_comp_demographics, # Map to function `plot_trend_comp_demographics()`
  
  .dem           = "gender", # Hold constant the `.dem` parameter
  data_frames    = df_list,  # Hold constant the `data_frames` parameter
  svry_dates     = survey_dates, # Hold constant the `svry_dates` parameter
  .facet_choice  = "Country", # Hold constant the `select_country` parameter
  .caption       = "Arab Barometer Wave VI, Algeria"
  )

```

Excellent!

The plots have been saved to a named list called `plots`. To access the plots for each variable, you can use the `$` and variable name.

```{r 08.21-Many-Graphs-Example2, fig.dim=c(13,12)}

# Trend graph for Q1COVID19
plots$Q1COVID19

# Trend graph for Q101
plots$Q101

# Trend graph for Q609
plots$Q609

```

You've done it! You have created many trend plots at once!