---
title: "ArabBarometR Graphing Guide"
author: "MaryClare Roche"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---

# Introduction {.unnumbered}

## Purpose {.unnumbered}

This guide is meant to give instructions on how to create graphs using the `ArabBarometR` package. If you do not yet have `ArabBarometR` installed, see either the README file on the package's GitHub repo, or [Installing and Updating `ArabBarometR`][Installing and Updating `ArabBarometR`] in the Appedix.

This guide was created using the **bookdown** package, which comes with many fun and useful features. An overview of these features can be found in the [Guide Features](https://arab-barometer.github.io/ArabBarometR-Guide/guide-features.html) section in the general `ArabBarometR` Guide.

As such, this guide assumes a few things:

-   That you have the `ArabBarometR` package installed on your machine.
    -   If this is not true, please take a look at the [README](https://github.com/Arab-Barometer/ArabBarometR#readme) file on the `ArabBarometR` GitHub page.
-   You have a basic understanding of how to load data and packages in R.
    -   If this is not true, you can pursue either [this guide](http://www.r-tutor.com/r-introduction/data-frame/data-import) or [this website](https://www.google.com/search?q=How+to+load+data+in+R&source=hp&ei=YKrYYb_1LLLH_Qanq6OICA&iflsig=ALs-wAMAAAAAYdi4cEgcmgRSgizOG8Zt8g7jSThX-RHp&ved=0ahUKEwi_pYruxKD1AhWyY98KHafVCIEQ4dUDCAk&uact=5&oq=How+to+load+data+in+R&gs_lcp=Cgdnd3Mtd2l6EAMyBQgAEIAEMgUIABCABDIFCAAQgAQyBQgAEIAEMgUIABCABDIFCAAQgAQyBQgAEIAEMgUIABCABDIGCAAQFhAeMgYIABAWEB46DgguEIAEELEDEMcBEKMCOgsIABCABBCxAxCDAToICAAQgAQQsQM6CwguEIAEEMcBEKMCOgUILhCABDoICC4QgAQQsQM6BQgAELEDUKAHWKIdYO4eaAFwAHgAgAFWiAGJCpIBAjIxmAEAoAEBsAEA&sclient=gws-wiz).

## General Guide Process {.unnumbered}

Assuming we are working with clean data, the graphs are created in two steps:

1.  Create a summary of the data you want to graph.
2.  Graph that summary.

For each type of graph, the guide will first go through how to create one graph, then how to create many graphs.

## Example Data {.unnumbered}

The examples in this guide will be created using data from Wave VI. For single survey graphs, it will use data from from Wave VI, Survey I. For trend graphs, it will use data from Wave VI, Survey I, II, and III, where Survey III is the final survey we conducted in Wave VI.

The Wave VI data can be found on [the Arab Barometer website](https://www.arabbarometer.org/survey-data/data-downloads/).

In order to create certain graphs (e.g., demographic graphs, comparative graphs for nominal questions, etc.), the data needs to be prepared correctly. The first chapter in this guide introduces several functions included in the `ArabBarometR` package that allow the user to easily prepare the data.

## Header Code {#headercode .unnumbered}

The code examples in this guide will **only** focus on how to create graphs. That is, the examples will not include loading and preparing the data or loading libraries. As you begin this guide, make sure your header looks something like the following:

```{r index-example-header,eval=FALSE}

setwd("/Path/to/Folder/with/Data")

library(ArabBarometR) # Our package
library(dplyr) # Lots of handy functions
library(purrr) # Mapping functions

survey1 <- haven::read.dta("Wave6Survey1.dta")
survey2 <- haven::read.dta("Wave6Survey2.dta")
survey3 <- haven::read.dta("Wave6Survey3.dta")

# Preparing Survey 1 data:
survey1 <- survey1 %>%
  
  age_demographic() %>%
  gender_demographic() %>%
  education_demographic() %>%
  income_demographic() %>%
  
  dummy_all(Q2061A)

# Preparing Survey 2 data:
survey2 <- survey2 %>%
  
  age_demographic() %>%
  gender_demographic() %>%
  education_demographic() %>%
  income_demographic() %>%
  
  dummy_all(Q2061A) %>%
  
  sjlabelled::add_labels(Q2061A, labels=c(`Economic situation` = 1,
                                          `Corruption` = 2,
                                          `Internal instability` = 6,
                                          `Foreign interference` = 7,
                                          `Public services` = 12,
                                          `COVID-19` = 15,
                                          `Other` = 16,
                                          `Don't know/refuse` = 98))

# Preparing Survey 3 data:
survey3 <- survey3 %>%
  
  # Adding Demographic Categories:
  age_demographic() %>%
  gender_demographic() %>%
  education_demographic() %>%
  income_demographic() %>%
  
  dummy_all(Q2061A) %>%
  
  sjlabelled::add_labels(Q2061A, labels=c(`Economic situation` = 1,
                                          `Corruption` = 2,
                                          `Internal instability` = 6,
                                          `Foreign interference` = 7,
                                          `Public services` = 12,
                                          `COVID-19` = 15,
                                          `Other` = 16,
                                          `Don't know/refuse` = 98))
```

In this code example **"/Path/to/Folder/with/Data"** is the path to where you are saving your work that *also contains your data*. This is best practice. For more on folders/working directories, see [Section 1.1.2](https://arab-barometer.github.io/ArabBarometR-Guide/installation.html) in the general Arab Barometer Guide.

**Wave6SurveyX.dta** in the above code example is a placeholder for whatever you have named the survey data for Surveys I, II, and III from Wave VI. If you read in the data (using the **haven::read.dta()** function) and save it as survey1, survey2, and survey3, you should be able to copy and paste the code in this guide exactly as is and run it in your own R session.

[Chapter 2](#chapter-1) introduces the functions used to prepare the data.


```{r index-load-packaged,include=FALSE}

library(ArabBarometR)
library(dplyr)
library(purrr)
library(ggplot2)

```

```{r index-load-w6s1, include=FALSE, cache=TRUE}

survey1 <- haven::read_dta("/Volumes/GoogleDrive/Shared drives/Arab Barometer/AB6/0. RELEASE FILES/Data Files/ENG Final Data Files FOR RELEASE/Arab_Barometer_Wave_6_Part_1_ENG_RELEASE_NOV_21.dta")

survey1 <- survey1 %>%
  
  age_demographic() %>%
  gender_demographic() %>%
  education_demographic() %>%
  income_demographic() %>%
  
  dummy_all(Q2061A)


```

```{r index-load-w6s2, include=FALSE, cache=TRUE}

survey2 <- haven::read_dta("/Volumes/GoogleDrive/Shared drives/Arab Barometer/AB6/0. RELEASE FILES/Data Files/ENG Final Data Files FOR RELEASE/Arab_Barometer_Wave_6_Part_2_ENG_RELEASE_gov.dta")

survey2 <- survey2 %>%
  
  # Adding Demographic Categories:
  age_demographic() %>%
  gender_demographic() %>%
  education_demographic() %>%
  income_demographic() %>%
  
  sjlabelled::add_labels(Q2061A, labels=c(`Economic situation` = 1,
                                          `Corruption` = 2,
                                          `Internal instability` = 6,
                                          `Foreign interference` = 7,
                                          `Public services` = 12,
                                          `COVID-19` = 15,
                                          `Other` = 16,
                                          `Don't know/refuse` = 98)) %>%
  
  dummy_all(Q2061A)
  

```

```{r index-load-w6s3, include=FALSE, cache=TRUE}

survey3 <- haven::read_dta("/Volumes/GoogleDrive/Shared drives/Arab Barometer/AB6/0. RELEASE FILES/Data Files/ENG Final Data Files FOR RELEASE/Arab_Barometer_Wave_6_Part_3_ENG_RELEASE_OCT_FIN.dta")

survey3 <- survey3 %>%
  
  # Adding Demographic Categories:
  age_demographic() %>%
  gender_demographic() %>%
  education_demographic() %>%
  income_demographic() %>%
  
  sjlabelled::add_labels(Q2061A, labels=c(`Economic situation` = 1,
                                          `Corruption` = 2,
                                          `Internal instability` = 6,
                                          `Foreign interference` = 7,
                                          `Public services` = 12,
                                          `COVID-19` = 15,
                                          `Other` = 16,
                                          `Don't know/refuse` = 98)) %>%
  
  
  dummy_all(Q2061A)

```
