# Using a `map()` {#using-map -}

Quite often in coding, you want to do the same thing only slightly differently many times. For example, make a graph for every variable in a data set.

The package `purrr` is full of functions designed to help you do just that.

In particular, the `map()` function is extremely handy. It is used in all examples related to making multiple graphs.

The map function takes two inputs: (1) a list of things to pass to a function, and (2) a function. Essentially, `map()` takes each item in the list, and passes it to the function very efficiently. 

## Functions with One Argument {#map-basics -}

Let's start with the basics.

Say we have a list of letters we want to capitalize, `"a","b","c","d"`. 

The function `toupper()` takes a string and capitalizes each letter in that string. Before learning about mapping, you might pass one string in at a time, like in the following code.

```{r map.1}

toupper("a")
toupper("b")
toupper("c")
toupper("d")

```

This is tedious and inefficient. Instead, with the map function, we can save our letters in a list and pass that list and the `toupper()` function to the `map()` function. Let's call our list of letters `L` and do just that.

```{r map.2}

L <- c("a","b","c","d") # List of letters

map(
  L,        # List object
  toupper   # Function
  )

```

Not only does this take fewer lines of code (which generally makes your code more legible), but at a large scale the `map()` function preforms *much* faster than running each line individually or even using a `for` loop.

## Functions with Multiple Arguments {#advanced-map - }

The basic example gives the basic idea of how `map()` works. In the context of using `map()` in combination with functions from the `ArabBarometR` package, however, you'll rarely have a function that takes only one argument. For example, `calculate_smry_individual()` *requires* at least two arguments: the data frame and the variable to calculate a summary for. If you are using the comparative data, you'll want to specify the country you're interested in as well.

Let's say we want to calculate summaries for every ordinal question in our data set for Algeria.

So how does `map()` know you want to feed `calculate_smry_individual()` a long list of questions while using the same data and country?

**It doesn't.**

**The user must tell `map()` which arguments to hold constant.**

If you look at the help page for `calculate_smry_individual()`^[Type `?ArabBarometR::calculate_smry_individual()` into your R console then hit enter.], under the section **Usage** you will see the following:

```{r map.3, eval=FALSE}

calculate_smry_individual(
  .ab,
  .var,
  .country = T,
  .weights = "WT",
  .language = "auto",
  .dkr = c(98, 99)
)

```

This is a list of all the arguments `calculate_smry_individual()` takes: `.ab`, `.var`, `.country`, `.weights`, `.language`, and `.dkr`. 

The `map()` function will try pass the items from the list as the first argument in the supplied function unless you tell it otherwise. In this case, the first argument is `.ab`, which should be the data frame. The following code will give you an error.

```{r map.4,error=TRUE}

# Pre-work to get ordinal questions:
ordinal_questions <- individual_titles$qname[individual_titles$qname %in% names(survey1) & individual_titles$type == "ordinal"]

# Using the mapping function:
map(
  ordinal_questions,         # List object
  calculate_smry_individual  # Function
)

```

The error says it occurs at `index 1`, the error was caused by `.f()`, and that "`argument ".var" is missing, with no default`." 

...What?

The first three lines of this error tell you **when**, **where**, and **why** the error occurred.

Index 1 tells us that that the very first item in `ordinal_questions` caused the error. You can see which variable that is with simple indexing as follows.

```{r map.5}

ordinal_questions[1]

```

Index 1 is telling us that the very first time a variable was passed to `calculate_smry_individual()`, an error occurred. 

Next, we know the error was caused by `.f()`. What's `.f()`? That is the second argument `map()` takes: the function. You can verify this by looking at the help page of `map()`. In our case, `.f()` is `calculate_smry_individual()`.

Now we know that the first time a variable was passed to `calculate_smry_individual()`, the function `calculate_smry_individual()` has an error.

Why? The error says `calculate_smry_individual()` needs a value for the argument `.var`, but none was provided.

Huh? We just passed a whole bunch of variables to `calculate_smry_individual()`, right?

**Wrong.**

Well. Kind of wrong.

We did pass a whole bunch of variables to `calculate_smry_individual()`, but the `map()` function thought we were passing a whole bunch of data frames. Since `.ab` is the first variable, `map()` tried to pass each item in `ordinal_questions` to `calculate_smry_individual()` as `.ab` while holding every other argument in `calculate_smry_individual()` constant. To `map()`, the function looks like `calculate_smry_individual(oridinal_questions, .var, T, "WT", "auto", c(98,99))`.

There are two problems with this.

1. Each item in `ordinal_questions` is not a data frame.
2. There is no default for `.var`, so there is nothing to hold constant.

Since `.var` has no default, R could not even attempt `calculate_smry_individual()`. That is why it is yelling at us saying there are no variables.

So how do we tell `map()` that `ordinal_questions` is a list of variables and that it needs to use `survey1` to give us summaries for Algeria? We need to tell `map()` that the argument `.ab` should always be `survey1` and the argument `.country` should always be `"Algeria"`.

```{r map.6, eval=FALSE}

map(
  ordinal_questions,         # List object
  calculate_smry_individual, # Function
  .ab = survey1,             # Constant argument 1
  .country = "Algeria"       # Constant argument 2
)

```

To `map()`, the function `calculate_smry_individual()` looks like `calculate_smry_individual(survey1, ordinal_questions, "Algeria", "WT", "auto", c(98,99))`. Much better.

As an exercise to the reader, how would we calculate these summaries if we wanted to include the value `100` in our "don't know/refuse" category?

The output of `map()` is list. Lists can be cumbersome. It is best to save this list as an object. You do that using the `<-` or `=`.

```{r map.7}

ordinal_summaries_list <- map(
  ordinal_questions,         
  calculate_smry_individual, 
  .ab = survey1,             
  .country = "Algeria"       
)

```

Now, you could reference an entry of `ordinal_summaries_list` one at a time, or feed it into another `map()`. For example, maybe you wanted to make a graph for each of these summaries.

## Conclusion

This concludes the brief "how-to" on `map()` from the `purrr` package. The `purrr` package contains many powerful variations on `map()`. To learn more about those variations, here are some more in-depth resources.

  - [A video by Hadley Wickham introducing `purrr`](https://www.youtube.com/watch?v=EGAs7zuRutY)
  - [Rebecca Barter's tutorial `purrr`](https://rebeccabarter.com/blog/2019-08-19_purrr) (this is very good and accessible)
  - [The main webpage for the `purrr` package](https://purrr.tidyverse.org/) (a bit technical)
  - [The `purrr` package cheat sheet](https://evoldyn.gitlab.io/evomics-2018/ref-sheets/R_purrr.pdf) (helpful once you know what you're doing)